### 2023-02-22 README.Rmd
update readme
update to readme, package file and class warning in checks

Using a simple spatstat example to generate a quasi-random scheme
```{r}
suppressPackageStartupMessages(library(spatstat))
data(simdat)
D <- rQuasi(100000,Window(simdat))
system.time(Q <- quadscheme(simdat,D,method="dirichlet", exact=FALSE))
```

@@

>>>>

Using a spatstat to generate a quasi-random scheme for the snails dataset.
```{r}
suppressPackageStartupMessages(library(spatstat))
e <- ext(covariates[[1]])
W <- owin(e[1:2],e[3:4])
snails_ppp <- ppp(presences[,1],presences[,2],W)
D <- rQuasi(100000,W)
system.time(Q <- quadscheme(snails_ppp,D,method="dirichlet", exact=FALSE))
```

@@

## Contributing Software
Fork the `ppmData` repository

Clone your fork using the command:

`git clone https://github.com/<username>/ppmData.git`

Contribute to your forked repository.

Create a pull request.

If your code passes the necessary checks and is documented, your changes 
and/or additions will be merged in the main `ppmData` repository.
